---
title: "Analyses"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---
```{r setup}
options(digits = 4)
options(scipen = 999)
```

Contrary to how I originally set up the analyses, doing inferential statistics with this small of sample is questionable. For example, look at how large the SD is for SSI acceptability of the Spanish version:

```{r example large SD}
filtered_baseline_data %>%
  filter(language == "Spanish") %>% 
  summarize(
    mean_total = mean(pi_pfs_sum),
    sd_total = sd(pi_pfs_sum),
    mean_item = mean_total / 7,
    sd_item = sd_total / 7)
```

A related note on inferential statistics and sample size from the Project YES pre-registration: "We will compute within-group effect size values (Cohen’s d, including 95% confidence intervals) reflecting change in pre-SSI to post-SSI levels of each immediate post-SSI outcome variable (hopelessness, self-hate, agency) for youths and adults, separately, if pre- and post-SSI data are available for at least 30 youth and at least 30 adult participants overall. We will compute within group effect size values separately as a function of SSI if post-SSI data are available for at least 30 youth for that SSI selection and at least 30 adults for that SSI selection." (https://osf.io/e52p3)

Another issue is that internal consistency for the Parent v Anorexia Scale is quite bad. Maybe this is because of the sample size and/or maybe the items don't conceptually make sense to sum (even with reverse scoring accounted for - others have reported below threshold internal consistency, see https://doi.org/10.1186/s40337-023-00869-x). It may be best to look at each item individually.

```{r internal consistency}
#The Parent vs Anorexia scale has very poor internal consistency
b_PAS_df <- filtered_baseline_data %>%
  select(b_PAS_1:b_PAS_7)
  alpha(b_PAS_df)
pi_PAS_df <- filtered_baseline_data %>%
  select(pi_PAS_1:pi_PAS_7)
  alpha(pi_PAS_df)
  
#Great internal consistency for the PEDEQ
b_PEDEQ_df <- filtered_baseline_data %>%
  select(b_PEDEQ_1, b_PEDEQ_2a, b_PEDEQ_3, b_PEDEQ_4, b_PEDEQ_5, b_PEDEQ_7, b_PEDEQ_9, b_PEDEQ_20, b_PEDEQ_22, b_PEDEQ_21, b_PEDEQ_6, b_PEDEQ_8, b_PEDEQ_10, b_PEDEQ_11, b_PEDEQ_24, b_PEDEQ_27, b_PEDEQ_28, b_PEDEQ_29, b_PEDEQ_12, b_PEDEQ_23, b_PEDEQ_25, b_PEDEQ_26) #only including the items that go into the global score
alpha(b_PEDEQ_df)

#Good internal consistnecy for DTS
b_DTS_df <- filtered_baseline_data %>% 
  select(b_DTS_1, b_DTS_2, b_DTS_3, b_DTS_4, b_DTS_5, b_DTS_6, b_DTS_7, b_DTS_8, b_DTS_9, b_DTS_10, b_DTS_11, b_DTS_12, b_DTS_13, b_DTS_14, b_DTS_15, b_DTS_16)
alpha(b_DTS_df)
```

It may be more useful to focus on reporting counts/percentages and the individual trajectories that participants followed (e.g., plot each participant's individual scores, reliable change index for individual clinically significant changes). A caveat though is that we should check internal consistency for all measures before deciding if RCI is even appropriate (ie we probably do not want to do it with PvA sum scores to begin with)

```{r descriptive statistics - overall sample, PVA summed}
#Parent v anorexia scale overall
PAS_stats <- filtered_baseline_data %>%
   drop_na(b_PAS_sum, pi_PAS_sum) %>%  #Two parents did not complete 
  select(b_PAS_sum, pi_PAS_sum) %>%
  mutate(PAS_sum_change_pre_post = pi_PAS_sum - b_PAS_sum) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Parent v anorexia scale English
PAS_stats_english <- filtered_baseline_data %>%
  filter(language == "English") %>% 
   drop_na(b_PAS_sum, pi_PAS_sum) %>%  #One parent did not complete 
  select(b_PAS_sum, pi_PAS_sum) %>%
  mutate(PAS_sum_change_pre_post = pi_PAS_sum - b_PAS_sum) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Parent v anorexia scale Spanish
PAS_stats_spanish <- filtered_baseline_data %>%
  filter(language == "Spanish") %>% 
   drop_na(b_PAS_sum, pi_PAS_sum) %>%  #One parent did not complete 
  select(b_PAS_sum, pi_PAS_sum) %>%
  mutate(PAS_sum_change_pre_post = pi_PAS_sum - b_PAS_sum) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Current distress 1 overall
distressnow_1_stats <- filtered_baseline_data %>%
  select(b_distressnow_1, pi_distressnow_1) %>%
  mutate(distressnow_1_change_pre_post = pi_distressnow_1 - b_distressnow_1) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Current distress 1 English
distressnow_1_stats_english <- filtered_baseline_data %>%
   filter(language == "English") %>% 
  select(b_distressnow_1, pi_distressnow_1) %>%
  mutate(distressnow_1_change_pre_post = pi_distressnow_1 - b_distressnow_1) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Current distress 1 Spanish
distressnow_1_stats_spanish <- filtered_baseline_data %>%
  filter(language == "Spanish") %>% 
  select(b_distressnow_1, pi_distressnow_1) %>%
  mutate(distressnow_1_change_pre_post = pi_distressnow_1 - b_distressnow_1) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Current distress 2 overall
distressnow_2_stats <- filtered_baseline_data %>%
  select(b_distressnow_2, pi_distressnow_2) %>%
  mutate(distressnow_2_change_pre_post = pi_distressnow_2 - b_distressnow_2) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Current distress 2 English
distressnow_2_stats_english <- filtered_baseline_data %>%
   filter(language == "English") %>% 
  select(b_distressnow_2, pi_distressnow_2) %>%
  mutate(distressnow_2_change_pre_post = pi_distressnow_2 - b_distressnow_2) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#Current distress 2 Spanish
distressnow_2_stats_spanish <- filtered_baseline_data %>%
  filter(language == "Spanish") %>% 
  select(b_distressnow_2, pi_distressnow_2) %>%
  mutate(distressnow_2_change_pre_post = pi_distressnow_2 - b_distressnow_2) %>%
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#DTS overall
DTS_stats <- filtered_baseline_data %>%
   drop_na(b_DTS_sum) %>%  #One parent did not complete 
  select(b_DTS_sum) %>% 
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#DTS English
DTS_stats_english <- filtered_baseline_data %>%
  filter(language == "English") %>%    
  select(b_DTS_sum) %>% 
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#DTS Spanish
DTS_stats_spanish <- filtered_baseline_data %>%
  filter(language == "Spanish") %>% 
  drop_na(b_DTS_sum) %>% #One parent did not complete
  select(b_DTS_sum) %>% 
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#PEDEQ global overall
P_EDEQ_stats <- filtered_baseline_data %>%
  filter(!Participant_ID %in% missing_pedeq_ids) %>%  #Six parents did not complete
  select(b_PEDEQ_global) %>% 
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#PEDEQ global English
PEDEQ_stats_english <- filtered_baseline_data %>%
  filter(language == "English", !Participant_ID %in% missing_pedeq_ids) %>% #Four parents did not complete
  select(b_PEDEQ_global) %>% 
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 

#PEDEQ global Spanish
PEDEQ_stats_spanish <- filtered_baseline_data %>%
  filter(language == "Spanish", !Participant_ID %in% missing_pedeq_ids) %>%  #Two parents did not complete
  select(b_PEDEQ_global) %>% 
  summarize(n = n(), 
            across(everything(),  list(mean = mean,  sd = sd))) 
```

```{r pre to post outcomes - overall sample, PVA summed}
#Parent v anorexia scale overall
t.test(filtered_baseline_data$pi_PAS_sum, filtered_baseline_data$b_PAS_sum, paired = TRUE)
d.dep.t.diff(mdiff = PAS_stats$PAS_sum_change_pre_post_mean,
             sddiff = PAS_stats$PAS_sum_change_pre_post_sd,
             n = PAS_stats$n,
             a = .05) %>%
  pluck("estimate")

#Current distress 1 overall
t.test(filtered_baseline_data$pi_distressnow_1, filtered_baseline_data$b_distressnow_1, paired = TRUE)
d.dep.t.diff(mdiff = distressnow_1_stats$distressnow_1_change_pre_post_mean,
             sddiff = distressnow_1_stats$distressnow_1_change_pre_post_sd,
             n = distressnow_1_stats$n,
             a = .05) %>%
  pluck("estimate")

#Current distress 2 overall
t.test(filtered_baseline_data$pi_distressnow_2, filtered_baseline_data$b_distressnow_2, paired = TRUE)
d.dep.t.diff(mdiff = distressnow_2_stats$distressnow_2_change_pre_post_mean,
             sddiff = distressnow_2_stats$distressnow_2_change_pre_post_sd,
             n = distressnow_2_stats$n,
             a = .05) %>%
  pluck("estimate")
```

```{r descriptive statistics and pre to post trajectory - individual level, PVA by item}

###Current Distress###
distress_now_1_individuals <- filtered_baseline_data %>% 
  select(Participant_ID, 
         language,
         b_distressnow_1,
         pi_distressnow_1)

distress_now_1_individuals_long <- distress_now_1_individuals %>% 
  pivot_longer(
    cols = c(b_distressnow_1, pi_distressnow_1),
    names_to  = "time",
    values_to = "score") %>% 
  mutate(
    time = recode(time,
                  b_distressnow_1  = "Pre",
                  pi_distressnow_1 = "Post"),
    time = factor(time, levels = c("Pre", "Post")),
    item = "Item 1")

distress_now_2_individuals <- filtered_baseline_data %>% 
  select(Participant_ID, 
         language,
         b_distressnow_2,
         pi_distressnow_2)

distress_now_2_individuals_long <- distress_now_2_individuals %>% 
  pivot_longer(
    cols = c(b_distressnow_2, pi_distressnow_2),
    names_to  = "time",
    values_to = "score") %>% 
  mutate(
    time = recode(time,
                  b_distressnow_2  = "Pre",
                  pi_distressnow_2 = "Post"),
    time = factor(time, levels = c("Pre", "Post")),
    item = "Item 2")

combined_distress_long <- bind_rows(distress_now_1_individuals_long, distress_now_2_individuals_long)

ggplot(combined_distress_long,
       aes(x = time, y = score,
           group = interaction(Participant_ID, item),
           color = language,
           shape = item)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  facet_wrap(~ Participant_ID) +
  theme_minimal(base_size = 10) +
  labs(
    x = NULL,
    y = "Preparedness",
    color = "Language",
    shape = "Item",
    title = "Pre-Post Preparedness to Manage Child's Distress"
  ) +
  scale_color_manual(values = c("English" = "steelblue", "Spanish" = "firebrick")) +
  scale_y_continuous(limits = c(0, 5)) +
  theme(strip.text = element_blank(),
        panel.spacing = unit(1, "lines"))

###Parent v Anorexia###
b_PAS_individual <- filtered_baseline_data %>%
  filter(!is.na(b_PAS_sum) & !is.na(pi_PAS_sum)) %>%  
  select(Participant_ID, language, b_PAS_1:b_PAS_7) %>%
  pivot_longer(
    cols = starts_with("b_PAS_"),
    names_to = "item",
    values_to = "score"
  ) %>%
  mutate(
    time = "Pre",
    item = str_remove(item, "^b_PAS_"),
    item = paste0("Item ", item))

pi_PAS_individual <- filtered_baseline_data %>%
  filter(!is.na(b_PAS_sum) & !is.na(pi_PAS_sum)) %>%  # Also here
  select(Participant_ID, language, pi_PAS_1:pi_PAS_7) %>%
  pivot_longer(
    cols = starts_with("pi_PAS_"),
    names_to = "item",
    values_to = "score"
  ) %>%
  mutate(
    time = "Post",
    item = str_remove(item, "^pi_PAS_"),
    item = paste0("Item ", item))

combined_PAS_long <- bind_rows(b_PAS_individual, pi_PAS_individual) %>%
  mutate(
    time = factor(time, levels = c("Pre", "Post")),
    item = factor(item, levels = paste0("Item ", 1:7)))

ggplot(combined_PAS_long,
       aes(x = time, y = score,
           group  = interaction(Participant_ID, item),
           color  = language,          
           shape  = item)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  facet_wrap(~ Participant_ID) +
  theme_minimal(base_size = 10) +
  labs(
    x = NULL,
    y = "Self-Efficacy",
    color = "Language",
    shape = "Item",
    title = "Pre-Post Parental Self-Efficacy"
  ) +
  scale_color_manual(values = c("English" = "steelblue",
                                "Spanish" = "firebrick")) +
  scale_shape_manual(values = 0:6) +  
  scale_y_continuous(limits = c(0, 5)) +
  theme(strip.text   = element_blank(),   
        panel.spacing = unit(1, "lines"))

###Distress Tolerance###

#Plot of each participant's baseline distress tolerance scores
filtered_baseline_data %>%
  filter(!is.na(b_DTS_sum)) %>%
  ggplot(aes(x = "", y = b_DTS_sum, color = language)) +
  geom_jitter(width = 0.2, height = 0, size = 3) +
  theme_minimal(base_size = 12) +
  labs(
    x = NULL,
    y = "Distress Tolerance Sum Score",
    title = "Distress Tolerance by Participant",
    color = "Language"
  ) +
  scale_color_manual(values = c("English" = "steelblue", "Spanish" = "firebrick")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

###Parent EDEQ ###

#Plot of each participant's baseline PEDEQ scores
filtered_baseline_data %>%
  filter(!Participant_ID %in% missing_pedeq_ids) %>%
  ggplot(aes(x = "", y = b_PEDEQ_global, color = language)) +
  geom_jitter(width = 0.2, height = 0, size = 3) +
  theme_minimal(base_size = 12) +
  labs(
    x = NULL,
    y = "PEDE-Q Global Score",
    title = "PEDE-Q by Participant",
    color = "Language"
  ) +
  scale_color_manual(values = c("English" = "steelblue", "Spanish" = "firebrick")) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
```
Really interesting and heterogeneous patterns for the PvA - I triple checked and all of the item (reverse) coding is correct such that higher scores are better. So maybe we are targeting some beliefs better than others (the pre-post increases)? Maybe even misrepresenting some ideas (the pre-post decreases)? Honestly, the direction for scoring some of these items conceptually confuses me / it's unlikely parents who completed Empower-ED would have learned this (e.g., item 5 - highest/best score is given when parent says "strongly agree" that their instincts should be trusted over expert advice )

```{r acceptability - overall sample}
#Acceptability total overall
filtered_baseline_data %>%
  summarize(
    mean_total = mean(pi_pfs_sum),
    sd_total = sd(pi_pfs_sum),
    mean_item = mean_total / 7,
    sd_item = sd_total / 7)

#Acceptability by item overall
filtered_baseline_data %>%
  select(pi_pfs_1:pi_pfs_7) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarize(mean = mean(value), 
            sd = sd(value))

#Acceptability total English
filtered_baseline_data %>%
  filter(language == "English") %>% 
  summarize(
    mean_total = mean(pi_pfs_sum),
    sd_total = sd(pi_pfs_sum),
    mean_item = mean_total / 7,
    sd_item = sd_total / 7)

#Acceptability by item English
filtered_baseline_data %>%
   filter(language == "English") %>% 
  select(pi_pfs_1:pi_pfs_7) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarize(mean = mean(value), 
            sd = sd(value))

#Acceptability total Spanish
filtered_baseline_data %>%
  filter(language == "Spanish") %>% 
  summarize(
    mean_total = mean(pi_pfs_sum),
    sd_total = sd(pi_pfs_sum),
    mean_item = mean_total / 7,
    sd_item = sd_total / 7)

#Acceptability by item Spanish
filtered_baseline_data %>%
   filter(language == "Spanish") %>% 
  select(pi_pfs_1:pi_pfs_7) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarize(mean = mean(value), 
            sd = sd(value))
```

```{r acceptability - individual level}
#Historgrams of acceptability ratings for each item
pfs_long <- filtered_baseline_data %>%
  filter(!is.na(pi_pfs_sum)) %>%
  select(Participant_ID, language, pi_pfs_1:pi_pfs_7) %>%
  pivot_longer(
    cols = starts_with("pi_pfs_"),
    names_to = "item",
    values_to = "score"
  ) %>%
  mutate(
    item = str_remove(item, "^pi_pfs_"),
    item = paste0("Item ", item),
    item = factor(item, levels = paste0("Item ", 1:7)))

ggplot(pfs_long, aes(x = score, fill = language)) +
  geom_bar(position = "dodge") +
  facet_wrap(~ item, ncol = 3) +
  theme_minimal(base_size = 12) +
  labs(
    x = "Acceptability Score",
    y = "Participant Count",
    fill = "Language",
    title = "Distribution of Acceptability Scores by Item"
  ) +
  scale_fill_manual(values = c("English" = "steelblue", "Spanish" = "firebrick")) +
  scale_x_continuous(breaks = 1:5) + 
  scale_y_continuous(breaks = seq(0, 25, 2)) +
    theme(panel.spacing = unit(1, "lines"))

#Plot of each participant's overall acceptability rating
pfs_average_scores <- filtered_baseline_data %>%
  filter(!is.na(pi_pfs_sum)) %>%
  mutate(
    acceptability_mean = pi_pfs_sum / 7
  ) %>%
  select(Participant_ID, language, acceptability_mean)

ggplot(pfs_average_scores, aes(x = "", y = acceptability_mean, color = language)) +
  geom_jitter(width = 0.2, height = 0, size = 3) +
  theme_minimal(base_size = 12) +
  labs(
    x = NULL,
    y = "Mean Acceptability Score",
    title = "Overall Acceptability by Participant",
    color = "Language"
  ) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 0.5)) +
  scale_color_manual(values = c("English" = "steelblue", "Spanish" = "firebrick")) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
```

```{r patterns of use}
###Completion of study activities###

baseline_data %>% 
  select(Participant_ID) %>% 
  count()
filtered_baseline_data %>% 
  select(Participant_ID) %>% 
  count()
#28 participants were invited, 25 were compensated/included per completion.

baseline_data %>% 
  filter(is.na(`Baseline Measures Complete`)) %>% 
  count()
baseline_data %>% 
  filter(is.na(`Intervention Complete`)) %>% 
  count()
baseline_data %>% 
  filter(is.na(`Post-Intervention Measures Complete`)) %>% 
  count()
#The 3 participants who were not compensated/included consented but never completed the baseline measures, intervention, or post-intervention measures.

filtered_baseline_data %>% 
  filter(is.na(`Baseline Measures Complete`)) %>% 
  count()
filtered_baseline_data %>% 
  filter(is.na(`Intervention Complete`)) %>% 
  count()
filtered_baseline_data %>% 
  filter(is.na(`Post-Intervention Measures Complete`)) %>% 
  count()
#Verifying that the 25 compensated/included participants passed all checkpoints (they did)

###Duration of SSI###

##Without handling outliers
names_in_order <- filtered_baseline_data %>%
  select(ends_with("Page Submit")) %>%
  names()

#Put mean duration and sd for each page into a new data frame
page_durations <- filtered_baseline_data %>% 
  select(ends_with("Page Submit")) %>%
    mutate(across(everything(), ~ as.numeric(as.character(.)))) %>%
  pivot_longer(cols = everything(),
               names_to = "page",
               values_to = "duration") %>%
  group_by(page) %>%
  summarise(mean_duration = mean(duration, na.rm = T),
            sd_duration = sd(duration,  na.rm = T), .groups = "drop") 
page_durations #the Mean and SD of seconds spent on each page of the SSI

#Summarize duration
mean_sd_durations <- page_durations %>%
  summarize(mean_duration_seconds = sum(mean_duration, na.rm = TRUE), 
            sd_duration_seconds = sum(sd_duration, na.rm = TRUE), 
            .groups = "drop") %>%
  mutate(mean_duration_minutes = mean_duration_seconds / 60,
         sd_duration_minutes = sd_duration_seconds / 60)
mean_sd_durations #huge SD even larger than the mean

##With handling outliers

#Look for outliers 
page_durations_long <- filtered_baseline_data %>% 
  select(ends_with("Page Submit")) %>%
  mutate(across(everything(), ~ as.numeric(as.character(.)))) %>%
  pivot_longer(cols = everything(),
               names_to = "page",
               values_to = "duration")
ggplot(page_durations_long, aes(x = page, y = duration)) +
  geom_boxplot(outlier.color = "red", outlier.shape = 16, outlier.size = 2) +
  theme_minimal() +
  labs(title = "Page Durations with Outliers",
       x = "Page",
       y = "Duration (seconds)")
#The data is super skewed with people keeping a page open for 1000+ seconds, so we will log transform it for visual clarity
ggplot(page_durations_long, aes(x = page, y = log(duration))) +
  geom_boxplot(outlier.color = "red", outlier.shape = 16, outlier.size = 2) +
  theme_minimal() +
  labs(title = "Page Durations with Outliers",
       x = "Page",
       y = "Log of Duration (seconds)")

#IQR method on raw data (not log transformed data)
page_durations_no_outliers <- page_durations_long %>%
  group_by(page) %>%
  mutate(
    Q1 = quantile(duration, 0.25, na.rm = TRUE),
    Q3 = quantile(duration, 0.75, na.rm = TRUE),
    IQR = Q3 - Q1,
    lower = Q1 - 1.5 * IQR,
    upper = Q3 + 1.5 * IQR) %>%
  ungroup() %>%
  filter(duration >= lower & duration <= upper)

page_durations_no_outliers_summary <- page_durations_no_outliers %>%
  group_by(page) %>%
  summarize(
    mean_duration = mean(duration, na.rm = TRUE),
    sd_duration = sd(duration, na.rm = TRUE),
    .groups = "drop"
  )

mean_sd_durations_no_outliers <- page_durations_no_outliers_summary %>%
  summarize(
    mean_duration_seconds = sum(mean_duration, na.rm = TRUE), 
    sd_duration_seconds = sum(sd_duration, na.rm = TRUE)
  ) %>%
  mutate(
    mean_duration_minutes = mean_duration_seconds / 60,
    sd_duration_minutes = sd_duration_seconds / 60
  )
mean_sd_durations_no_outliers
```

```{r demographics}
filtered_baseline_data %>%
  count(dem_ethnicity) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_relationship) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_momdad) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_marital) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_caretaking) %>%
  mutate(percent = (n / sum(n))*100)

#Only asked if dem_caretaking is Yes/1
filtered_baseline_data %>%
  count(dem_live) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_income) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_familyhx) %>%
  mutate(percent = (n / sum(n))*100)

#Age as categories
filtered_baseline_data %>%
  count(dem_childage) %>%
  mutate(percent = (n / sum(n))*100)

#Age as mean/SD
filtered_baseline_data %>% 
  summarise(mean = mean(dem_childage, na.rm = TRUE),
            sd = sd(dem_childage, na.rm = TRUE))

filtered_baseline_data %>%
  count(dem_childgrade) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_childsex) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  select(starts_with("dem_childgender")) %>% 
  summarize(across(everything(), 
                   list(n = ~ sum(. == 1),
                        percent = ~ mean(. == 1) * 100))) #child gender is select all that apply

filtered_baseline_data %>%
  count(dem_childethnicity) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_childinsurance) %>%
  mutate(percent = (n / sum(n))*100)

#Only asked if dem_childinsurance is Yes/1
filtered_baseline_data %>%
  count(dem_insurancetype) %>%
  mutate(percent = (n / sum(n))*100)

#Only asked if dem_childinsurance is Yes/1
filtered_baseline_data %>%
  count(dem_coverage) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_outofpocket) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>%
  count(dem_childEDtx) %>%
  mutate(percent = (n / sum(n))*100)

#Only asked if dem_childEDtx is Yes/1
filtered_baseline_data %>%
  select(starts_with("dem_txtype")) %>% 
  summarize(across(everything(), 
                   list(n = ~ sum(. == 1),
                        percent = ~ mean(. == 1) * 100))) #EDtx type is select all that apply

filtered_baseline_data %>%
  count(dem_medical) %>%
  mutate(percent = (n / sum(n))*100)

filtered_baseline_data %>% 
  summarise(mean = mean(dem_admitlength, na.rm = TRUE),
            sd = sd(dem_admitlength, na.rm = TRUE))

filtered_baseline_data %>% 
  summarise(mean = mean(dem_admitbmi, na.rm = TRUE),
            sd = sd(dem_admitbmi, na.rm = TRUE))

filtered_baseline_data %>%
  select(starts_with("dem_psych")) %>% 
  summarize(across(everything(), 
                   list(n = ~ sum(. == 1),
                        percent = ~ mean(. == 1) * 100))) #co-occuring psych is select all that apply
```